---
title: "Berries Project"
author: "Yuxi Wang"
date: "2020/10/11"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(
  "tidyverse"
)
```

## 1 Data Cleaning
### 1.1 Data Import
After downloading data from the National Agriculture Statistics Service (NASS) of United States Department of Agriculture(USDA), we have the dataset containinig information about three types of berries: Blueberries, Strawberries and Raspberries. 

Since there are only 8 out 21 columns that are useful for further analysis, we will drop those first for simplicity of the dataset.
```{r}
dt <- read.csv(file="/Users/mac/Desktop/berries.csv",header=T)
berry_raw <- dt %>%
  select(Year,Period,State,Commodity,Data.Item,Domain,Domain.Category,Value)
head(berry_raw)
```

### 1.2 Initial Screening of the Data

From the output above, we can notice that there are a lot of categorical varibles. However, `Value` is supposed to be a numeric varible according to the defination on the website.

By looking at the column of `Value`, many (D),(NA),(X) and (Z) appears to be the reason why this column is defined as categorical. So, we will replace those with NA.

```{r}
berry_raw$Value <- as.numeric(berry_raw$Value)
# Replace (D),(NA),(X) and (Z) with NA
berry_raw[berry_raw =="(D)"] <- NA
berry_raw[berry_raw =="(NA)"] <- NA
berry_raw[berry_raw =="(X)"] <- NA
berry_raw[berry_raw =="(Z)"] <- NA
```

Since those irregular "NA"s have been replaced, a summary of the dataset should be made for further exploration of the data.
```{r}
# Summary of berry_raw
summary(berry_raw)
view(berry_raw)
```

### 1.3 Further Data Cleaning on Blueberries
After finishing the initial screening of the dataset, we use the `filter` function to extract data of strawberry to conduct further study. The summary of the strawberry dataset shows that there are 4958 NAs in the column `Value`. Since those observations does not contain much information, we choose to delete them.

#### 1.3.1 Cleaning: `Data Item`
```{r}
strawberry_raw <- berry_raw %>% filter(Commodity=="STRAWBERRIES")
# Summary of the dataset
summary(strawberry_raw)
```

```{r}
strawberry_raw2 <- strawberry_raw %>% drop_na()
item_pre <- strawberry_raw2$Data.Item
# Replace "-" with "," for the convenience of spliting
item <- gsub(" - ",",",item_pre)
view(item)
```

```{r}
# Type of the strawberry
type_stberry <- str_extract_all(item,"(BEARING){1}")
```


#### 1.3.2 Cleaning: `Domain Category`
Then, we will separate the chemical type and the detail of certain kind of chemical from the column `Domain Category` by using `separate` function in tidyverse package.

```{r warning=FALSE}
chemical_obj <- data.frame(strawberry_raw2$Domain.Category)
```


#### 2 EDA of the data
#### 2.1 exploring the hole data set
#### 2.1.1 summarize data by grouping "measurement"
Since we can find the measurement of each data are different, we need to group them and summarize them.
```{r warning=FALSE}
# Measurement of the strawberry
strawberry_raw2$unit <- str_extract_all(item,"MEASURED IN.*[^, /AVG]|ACRES.*")
# Also, we have to delate the comma and space
strawberry_raw2$unit <- str_replace(strawberry_raw2$unit,",","")
strawberry_raw2$unit <- trimws(strawberry_raw2$unit)
strawberry_raw2$unit <- as.character(strawberry_raw2$unit)
strawberry_sum <- strawberry_raw2 %>%
  group_by(unit)%>%
  summarize(
    count=n(),
    value=sum(Value)
    )
view(strawberry_raw2)
print(strawberry_sum)
```

#### 2.1.2 Since we know that their are 13 measurements of the Value, we first plot the total plot of all these item.
```{r}
ggplot(data = strawberry_sum, mapping = aes(x = unit, y = count))+
   geom_point(shape=21,fill="black", alpha = 1/3)

ggplot(data = strawberry_sum, mapping = aes(x = unit, y = value, size = count)) +
  geom_point(shape=21,fill="cornsilk", alpha = 1/3) 
```
The first plot shows that the number of each measurement. While the second plot show that the value of each measurement. this has a little meaning, but I think we have to have a roughly knowledge of the value of each measurement. The huge difference can show why I need to separate the "item" variable.

#### 2.2.1 Creat a new frame in order to exact data to do the further EDA
```{r}
# Creat a new data.frame in order to exact data to do the further EDA
strawberry_unit <- strawberry_raw2 %>%
  group_by(unit)%>%
  summarize(
    state=State,
    year= Year,
    count=n(),
    value=Value
    )
view(strawberry_unit)
```

To make a box plot
This plot is just let us have a knowledge that which measurement can be use as a variable in the futher exploring analysis. Since the data that are have much outliers or the range of the data are not great can make a misunderstanding of the model.
```{r}
# excluding outliers
boxplot <- ggplot(strawberry_unit, aes(x = unit, y = value, fill=unit))+ 
  geom_boxplot(outlier.colour = NA,notch = TRUE) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1),
        axis.text = element_text(size = 7),
        axis.title = element_text(size = 13, face = "bold")) +
  coord_cartesian(ylim = c(0, 1000)) +
  guides(fill=FALSE)
print(boxplot)
```


#### 2.2.2 Creat the data.frame that only contain the $/CWT
```{r}
strawberry_unit_CWT <- filter(strawberry_unit,unit=="MEASURED IN $ / CWT" )
strawberry_unit_CWT$value <- as.numeric(strawberry_unit_CWT$value)
strawberry_unit_CWT$value[strawberry_unit_CWT$value ==0] <- NA # Replace 0 with NA
strawberry_unit_CWT_new <- group_by(strawberry_unit_CWT,year,state)
strawberry_CWT <- summarize(strawberry_unit_CWT_new, value = mean(value, na.rm = TRUE))
summary(strawberry_CWT)
```
# Making a plot that the x-label is year, the y-label is value and different color means difference states.
```{r}
# Plot $/ CWT plot 
ggplot(strawberry_CWT, aes(x = year, y = value, fill=state)) +
   geom_bar(stat = "identity")

```
```{r}
# We can also transfer the plot in other way
ggplot(strawberry_CWT, aes(x =state , y = value, fill=year)) +
   geom_bar(stat = "identity")+
   theme(axis.text.x = element_text(angle = 60, hjust = 1),
        axis.text = element_text(size = 11),
        axis.title = element_text(size = 13, face = "bold"))
```
By looking at these two plots, the we can have more insight of the data that use $ /cwt as measurement.

#### 2.2.3 To find the outliers of the $/CWT
```{r}
# excluding outliers
outliers <- ggplot(strawberry_CWT, aes(x =state, y = value,fill=state))
outliers <- outliers + 
  geom_boxplot(width=0.5, outlier.colour = NA) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1),
        axis.text = element_text(size = 11),
        axis.title = element_text(size = 13, face = "bold")) +
  coord_cartesian(ylim = c(0, 250)) +
  labs(x = "strawberry_CWT of year")+
  guides(fill= FALSE)
print(outliers)
```
By looking at this plot, there are servel states that the data of tem are not very great. However, since I have not separate the year of the variable.


#### 2.3 After analysising the dwt variable, the MEASURED IN LB / ACRE / APPLICATION is also important, so I make a plot.
#### 2.3.1 tidy data 
```{r}
# tidy the data
strawberry_unit_APPLICATION <- filter(strawberry_unit,unit=="MEASURED IN LB / ACRE / APPLICATION" )
strawberry_unit_APPLICATION$value <- as.numeric(strawberry_unit_APPLICATION$value)
strawberry_unit_APPLICATION$value[strawberry_unit_APPLICATION$value ==0] <- NA # Replace 0 with NA
strawberry_unit_APPLICATION_new <- group_by(strawberry_unit_APPLICATION,year,state)
strawberry_APPLICATION <- summarize(strawberry_unit_APPLICATION_new, value = mean(value, na.rm = TRUE))

```

```{r}
# Plot MEASURED IN LB / ACRE / APPLICATION plot 
ggplot(strawberry_APPLICATION, aes(x = year, y = value, fill=state)) +
   geom_bar(stat = "identity")
```
In this plot, we can find that there are no data in 2017, so we would better not to use year as a main variable.

```{r}
# We can also transfer the plot in other way
ggplot(strawberry_APPLICATION, aes(x =state , y = value, fill=year)) +
   geom_bar(stat = "identity")+
   theme(axis.text.x = element_text(angle = 60, hjust = 1),
        axis.text = element_text(size = 11),
        axis.title = element_text(size = 13, face = "bold"))
```
# In this plot we can just have a view of these three states, since other states are not involved in the data set for MEASURED IN LB / ACRE / APPLICATION.
```{r}
# excluding outliers
outliers <- ggplot(strawberry_APPLICATION, aes(x =state, y = value,fill=state))
outliers <- outliers + 
  geom_boxplot(width=1, outlier.colour = NA) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1),
        axis.text = element_text(size = 11),
        axis.title = element_text(size = 13, face = "bold")) +
  coord_cartesian(ylim = c(0, 15)) +
  labs(x = "strawberry_CWT of year")+
  guides(fill= FALSE)
print(outliers)
```
We can find whether there are outliers in the plot.

#### 3 Shiny part
#### 3.1 Using shiny to make the strewberry data as a chart
```{r}
library(shiny)
library(tidyverse)

dt <- read.csv(file="/Users/mac/Desktop/berries.csv",header=T)
berry_raw <- dt %>%
    select(Year,Period,State,Commodity,Data.Item,Domain,Domain.Category,Value)

berry_raw$Value <- as.numeric(berry_raw$Value)
# Replace (D),(NA),(X) and (Z) with NA
berry_raw[berry_raw =="(D)"] <- NA
berry_raw[berry_raw =="(NA)"] <- NA
berry_raw[berry_raw =="(X)"] <- NA
berry_raw[berry_raw =="(Z)"] <- NA
strawberry_raw <- berry_raw %>% filter(Commodity=="STRAWBERRIES")
strawberry_raw2 <- strawberry_raw %>% drop_na()
item_pre <- strawberry_raw2$Data.Item
# Replace "-" with "," for the convenience of spliting
item <- gsub(" - ",",",item_pre)
# Type of the strawberry
type_stberry <- str_extract_all(item,"(BEARING){1}")
strawberry_raw2$unit <- str_extract_all(item,"MEASURED IN.*[^, /AVG]|ACRES.*")
# Also, we have to delate the comma and space
strawberry_raw2$unit <- str_replace(strawberry_raw2$unit,",","")
strawberry_raw2$unit <- trimws(strawberry_raw2$unit)
strawberry_raw2$unit <- as.character(strawberry_raw2$unit)
strawberry_sum <- strawberry_raw2 %>%
    group_by(unit)%>%
    summarize(
        count=n(),
        value=sum(Value)
    )



# Shiny app
strawberry_unit <- as.data.frame(strawberry_unit)
ui <- fluidPage(
    title = "Strawberry Data Tables",
    mainPanel(
        tabsetPanel(
            id = 'dataset',
            tabPanel("strawberry data",
                     
                     # Create a new Row in the UI for selectInputs
                     fluidRow(
                         column(4,
                                selectInput("measurement",
                                            "kinds of measurement:",
                                            c("All",
                                              unique(as.character(strawberry_unit$unit))))
                         ),
                         column(4,
                                selectInput("year",
                                            "Year:",
                                            c("All",
                                              unique(strawberry_unit$year)))
                         ),
                         column(4,
                                selectInput("state",
                                            "State:",
                                            c("All",
                                              unique(strawberry_unit$state)))
                         ),
                     ),
                     # Create a new row for the table.
                     DT::dataTableOutput("table1")))
        
    )
)


server <- function(input, output) {
    strawberry_unit$unit <- as.character(strawberry_unit$unit)
    strawberry_unit$year <- as.numeric(strawberry_unit$year)
    strawberry_unit$state <- as.character(strawberry_unit$state)
    # Filter data based on selections
    output$table1 <- DT::renderDataTable(
        DT::datatable({
            data <- strawberry_unit
            
            if (input$year != "All") {
                data <- data[data$year == input$year,]
            }
            
            
            
            data
        }))
    
    
}

# Run the application 
shinyApp(ui = ui, server = server)
```





#### 3.2 Using shiny to plot the EDA process.
```{r}
library(shiny)
library(tidyverse)
library(reshape2)
library(data.table)
Sys.setlocale("LC_TIME", "English")

dt <- read.csv(file="/Users/mac/Desktop/berries.csv",header=T)
berry_raw <- dt %>%
    select(Year,Period,State,Commodity,Data.Item,Domain,Domain.Category,Value)

berry_raw$Value <- as.numeric(berry_raw$Value)
# Replace (D),(NA),(X) and (Z) with NA
berry_raw[berry_raw =="(D)"] <- NA
berry_raw[berry_raw =="(NA)"] <- NA
berry_raw[berry_raw =="(X)"] <- NA
berry_raw[berry_raw =="(Z)"] <- NA
strawberry_raw <- berry_raw %>% filter(Commodity=="STRAWBERRIES")
strawberry_raw2 <- strawberry_raw %>% drop_na()
item_pre <- strawberry_raw2$Data.Item
# Replace "-" with "," for the convenience of spliting
item <- gsub(" - ",",",item_pre)
# Type of the strawberry
type_stberry <- str_extract_all(item,"(BEARING){1}")
strawberry_raw2$unit <- str_extract_all(item,"MEASURED IN.*[^, /AVG]|ACRES.*")
# Also, we have to delate the comma and space
strawberry_raw2$unit <- str_replace(strawberry_raw2$unit,",","")
strawberry_raw2$unit <- trimws(strawberry_raw2$unit)
strawberry_raw2$unit <- as.character(strawberry_raw2$unit)
strawberry_sum <- strawberry_raw2 %>%
    group_by(unit)%>%
    summarize(
        count=n(),
        value=sum(Value)
    )
strawberry_unit <- strawberry_raw2 %>%
    group_by(unit)%>%
    summarize(
        state=State,
        year= Year,
        count=n(),
        value=Value
    )
strawberry_unit_CWT <- filter(strawberry_unit,unit=="MEASURED IN $ / CWT" )
strawberry_unit_CWT$value <- as.numeric(strawberry_unit_CWT$value)
strawberry_unit_CWT$value[strawberry_unit_CWT$value ==0] <- NA # Replace 0 with NA
strawberry_unit_CWT_new <- group_by(strawberry_unit_CWT,year,state)
strawberry_CWT <- summarize(strawberry_unit_CWT_new, value = mean(value, na.rm = TRUE))
strawberry_unit_APPLICATION <- filter(strawberry_unit,unit=="MEASURED IN LB / ACRE / APPLICATION" )
strawberry_unit_APPLICATION$value <- as.numeric(strawberry_unit_APPLICATION$value)
strawberry_unit_APPLICATION$value[strawberry_unit_APPLICATION$value ==0] <- NA # Replace 0 with NA
strawberry_unit_APPLICATION_new <- group_by(strawberry_unit_APPLICATION,year,state)
strawberry_APPLICATION <- summarize(strawberry_unit_APPLICATION_new, value = mean(value, na.rm = TRUE))


# Define UI ----
ui <- fluidPage(
    titlePanel("Analysis of Berries Dataset"),
    verticalLayout(
        mainPanel(
            h3("1. Overview of the classification of the measurement."),
            h4("1.1 two point plot of the measurement"),
            h5("Having a roughly knowledge of the value of each measurement after grouping the measurement"),
            plotOutput("p1"),
            plotOutput("p2"),
            h5("The first plot shows that the number of each measurement. While the second plot show that the value of each measurement. this has a little meaning, but I think we have to have a roughly knowledge of the value of each measurement. The huge difference can show why I need to separate the 'item' variable."),
            
            h4("1.2 Box plot of each knid of measurement"),
            h5("A box plot."),
            plotOutput("p3"),
            h5("This plot is just let us have a knowledge that which measurement can be use as a variable in the futher exploring analysis. Since the data that are have much outliers or the range of the data are not great can make a misunderstanding of the model."),
           
            h3("2. EDA for the measurement is  $/CWT"),
            h4("2.1 Bar plot of Year"),
            plotOutput("p4"),
            h5("Making a plot that the x-label is year, the y-label is value and different color means difference states."),

            h4("2.2  Bar plot of state"),
            plotOutput("p5"),
            h5("Making a plot that the x-label is each state, the y-label is value and different color means difference years."),
           
            h4("2.3 box plot of state"),
            plotOutput("p6"),
            h5("By looking at this plot, there are servel states that the data of tem are not very great. However, since I have not separate the year of the variable.")
        )  
    )
)

# Define server logic required to draw a plot
server <- function(input, output) {
    output$p1 <- renderPlot({
        ggplot(data = strawberry_sum, mapping = aes(x = unit, y = count))+
            geom_point(shape=21,fill="black", alpha = 1/3)
    })
    
    output$p2 <- renderPlot({
        ggplot(data = strawberry_sum, mapping = aes(x = unit, y = value, size = count)) +
            geom_point(shape=21,fill="cornsilk", alpha = 1/3) 
    })
    output$p3 <- renderPlot({
        ggplot(strawberry_unit, aes(x = unit, y = value, fill=unit))+ 
            geom_boxplot(outlier.colour = NA,notch = TRUE) +
            theme(axis.text.x = element_text(angle = 60, hjust = 1),
                  axis.text = element_text(size = 7),
                  axis.title = element_text(size = 13, face = "bold")) +
            coord_cartesian(ylim = c(0, 1000)) +
            guides(fill=FALSE)
    })

    output$p4 <- renderPlot({
        ggplot(strawberry_CWT, aes(x = year, y = value, fill=state)) +
            geom_bar(stat = "identity")
    })
    output$p5 <- renderPlot({
        ggplot(strawberry_CWT, aes(x =state , y = value, fill=year)) +
            geom_bar(stat = "identity")+
            theme(axis.text.x = element_text(angle = 60, hjust = 1),
                  axis.text = element_text(size = 11),
                  axis.title = element_text(size = 13, face = "bold"))
    })
    output$p6 <- renderPlot({
        ggplot(strawberry_CWT, aes(x =state, y = value,fill=state))+ 
            geom_boxplot(width=0.5, outlier.colour = NA) +
            theme(axis.text.x = element_text(angle = 60, hjust = 1),
                  axis.text = element_text(size = 11),
                  axis.title = element_text(size = 13, face = "bold")) +
            coord_cartesian(ylim = c(0, 250)) +
            labs(x = "strawberry_CWT of year")+
            guides(fill= FALSE)
    })

}

# Run the application 
shinyApp(ui = ui, server = server)

```


